% Preamble
% ---
\documentclass{article}

% Packages
% ---
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage{hyperref} % Add a link to your document
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    citecolor=blue,      
    urlcolor=blue,
}
\usepackage{graphicx} % Add pictures to your document
\usepackage{listings} % Source code formatting and highlighting
\usepackage{framed} % Source code formatting and highlighting
\usepackage{appendix} % Source code formatting and highlighting
\usepackage[automake]{glossaries}
\usepackage{csquotes}
\usepackage[letterpaper, portrait, margin=1.5in]{geometry}

\graphicspath{ {images/} }

\newglossaryentry{sentinel}
{
    name={Sentinel},
    description={A Sentinel is a heuristic witnesses. It observes heuristics and vouches for the certainty and accuracy of them by producing temporal ledgers. The most important aspect of a Sentinel is that it produces ledgers that Diviners can be certain came from the same source by adding Proof of Origin to them}
}

\newglossaryentry{bridge}
{
    name={Bridge},
    description={A Bridge is a heuristic transcriber. It securely relays heuristic ledgers from Sentinels to Diviners. The most important aspect of a Bridge is that a Diviner can be sure that the heuristic ledgers that are received from a Bridge have not been altered in any way. The second most important aspect of a Bridge is that they add an additional Proof of Origin metadata}
}

\newglossaryentry{archivist}
{
    name={Archivist},
    description={An Archivist stores heuristics as a part of the decentralized data set with the goal of having all historical ledgers stored, but without that requirement. Even if some data is lost or becomes temporarily unavailable, the system continues to function, just with reduced accuracy. Archivists also index ledgers so that they can return a string of ledger data if needed. Archivists store raw data only and get paid solely for retrieval of the data. Storage is always free}
}

\newglossaryentry{diviner}
{
    name={Diviner},
    description={A Diviner answers a given question by analyzing historical data that has been stored by the XYO Network. Heuristics stored in the XYO Network must have a high level of Proof of Origin to determine the validity and accuracy of the heuristic. A Diviner obtains and delivers an answer by judging the witness based on its Proof of Origin. Given that the XYO Network is a trustless system, Diviners must be incentivized to provide honest analyses of heuristics. Unlike Sentinels and Bridges, Diviners use Proof of Work to add answers to the blockchain}
}

\newglossaryentry{gas}
{
    name={gas},
    description={The cost of a transaction (i.e. question) in the form of XYO Tokens}
}

\newglossaryentry{proof-of-origin}
{
    name={Proof of Origin},
    description={Proof of Origin is the key to verifying that ledgers flowing into the XYO Network are valid. A unique ID for source of data is not practical since it can be forged. Private Key signing is not practical since most parts of the XYO Network are difficult or impossible to physically secure, thus the potential for a bad actor to steal a Private Key is too feasible. To solve this, XYO Network uses Transient Key Chaining. The benefit of this is that it is impossible to falsify the chain of origin for data. However, once the chain is broken, it is broken forever and cannot be continued, rendering it an island}
}

\newglossaryentry{proof-of-work}
{
    name={Proof of Work},
    description={Proof of Work is a piece of data that satisfies certain requirements, is difficult to produce (i.e. costly, time-consuming), but easy for others to verify. Producing a Proof of Work can be a random process with a low probability of generation so that rigorous trial and error is required on average before a valid Proof of Work is created}
}

\newglossaryentry{bound-witness}
{
    name={Bound Witness},
    description={Bound Witness is a concept achieved by the existence of a bidirectional heuristic. Given that an untrusted source of data for the use of digital contract resolution (an oracle) is not useful, there is a substantial increase in certainty of the data provided by the establishment of such a heuristic. The primary bidirectional heuristic is proximity since both parties can validate the occurrence and range of an interaction by cosigning the interaction. This allows for a zero-knowledge proof that the two nodes were in proximity of each other.}
}

\newglossaryentry{smart-contract}
{
    name={smart contract},
    description={A protocol coined by Nick Szabo before Bitcoin, purportedly in 1994 (which is why some believe him to be Satoshi Nakamoto, the mystical and unknown inventor of Bitcoin). The idea behind smart contracts is to codify a legal agreement in a program and to have decentralized computers execute its terms, instead of humans having to interpret and act on contracts. Smart contracts collapse money (e.g. Ether) and contracts into the same concept. Being that smart contracts are deterministic (like computer programs) and fully transparent and readable, they serve as a powerful way to replace middle-men and brokers}
}

\newglossaryentry{cryptoeconomics}
{
    name={cryptoeconomics},
    description={A formal discipline that studies protocols that govern the production, distribution, and consumption of goods and services in a decentralized digital economy. Cryptoeconomics is a practical science that focuses on the design and characterization of these protocols}
}

\newglossaryentry{xyo-network}
{
    name={XYO Network},
    description={XYO Network stands for ``XY Oracle Network.'' It is comprised of the entire system of XYO enabled components/nodes that include Sentinels, Bridges, Archivists, and Diviners. The primary function of the XYO Network is to act as a portal by which digital smart contracts can be executed through real world geo-location confirmations}
}

\newglossaryentry{certainty}
{
    name={certainty},
    description={A measure of the likelihood that a data point or heuristic is free from corruption or tampering}
}

\newglossaryentry{accuracy}
{
    name={accuracy},
    description={A measure of confidence that a data point or heuristic is within a specific margin of error}
}

\newglossaryentry{oracle}
{
    name={oracle},
    description={A part of a DApp (decentralized application) system that is responsible for resolving a digital contract by providing an answer with accuracy and certainty. The term ``oracle'' originates from cryptography where it signifies a truly random source (e.g. of a random number). This provides the necessary gate from a crypto equation to the world beyond. Oracles feed smart contracts information from beyond the chain (the real world, or off-chain). Oracles are interfaces from the digital world to the real world. As a morbid example, consider a contract for a Last Will \& Testament. A Will's terms are executed upon confirmation that the testator is deceased. An oracle service could be built to trigger a Will by compiling and aggregating relevant data from official sources. The oracle could then be used as a feed or end-point for a smart contract to call out to in order to check whether or not the person is deceased}
}

\newglossaryentry{heuristic}
{
    name={heuristic},
    description={A data point about the real world relative to the position of a Sentinel (proximity, temperature, light, motion, etc...)}
}

\newglossaryentry{transient-key-chain}
{
    name={Transient Key Chain},
    description={A Transient Key Chain links a series of data packets using Transient Key Cryptography}
}

\newglossaryentry{best-answer-score}
{
    name={Best Answer Score},
    description={A score generated by a Best Answer Algorithm that ranks the quality of the score.  The higher the score, the better it is, per the algorithm.  This score is used to determine which answer is better given two analyzed answers}
}

\newglossaryentry{best-answer-algorithm}
{
    name={Best Answer Algorithm},
    description={An algorithm used to generate Best Answer Scores when a Diviner chooses an answer.  The XYO Network permits the addition of specialized algorithms and allows the customer to specify which algorithm to use.  It is required that this algorithm will result in the same score when run on any Diviner given the same data set}
}

\newglossaryentry{origin-chain-score}
{
    name={Origin Chain Score},
    description={The score assigned to an Origin Chain to determine its credibility. This assessment takes length, tangle, overlap, and redundancy into consideration}
}

\newglossaryentry{origin-chain}
{
    name={Origin Chain},
    description={A Transient Key Chain that links together a series of Bound Witness heuristic ledger entries}
}

\newglossaryentry{origin-tree}
{
    name={Origin Tree},
    description={A data set of ledger entries taken from various Origin Chains to establish the origin of a heuristic ledger entry with a specified level of certainty}
}

\newacronym{pow}{PoW}{Proof of Work}

\newacronym{poo}{PoO}{Proof of Origin}

\newacronym{xy-oracle-network}{XY Oracle Network}{XYO Network}


\makeglossary

\title {XYO Network in Automated Drone Technology}
\author{Johnny Kolasinski, Christine Sako}
\date{January 2018}

\begin{document}
\maketitle
\tableofcontents

\begin{center}
\line(1,0){50}
\end{center}

\begin{abstract}
There has been significant buzz recently around drone technology and the role it will play in our future. From emergency medical supply delivery to one-hour eCommerce delivery, advancements in drone automation bring these applications closer to reality each day. This raises very valid and practical questions for both the entities that will use drone technology and those affected by it. Where will the drones be able to fly? How will accidents be prevented? How will package delivery be confirmed? The \Gls{xy-oracle-network} can provide independently verified location data that can help keep drones within approved flight paths, avoid collisions with both moving and stationary objects, and report package location at key points. According to Amazon CEO Jeff Bezos, the platform's current plans for delivery confirmation require the customer to print out their own pre-generated symbol from a physical printer \cite{nickelsburg-amazondrones}. The \Gls{xyo-network} provides trustless location verification that eliminates this requirement, making the overall process and user experience smoother for the customer. The integration of the \Gls{xyo-network}'s unique blockchain technology will maximize the efficiency of the implemented drone systems, which is imperative for all newly-established industries to thrive and scale.

\end{abstract}

\begin{center}
\line(1,0){50}
\end{center}

\section {Problem}
Numerous entities are very close to implementing automated drone services, from eCommerce giants like Amazon and Walmart to Google/Alphabet's Project Wing to the numerous drone mapping services already in operation. Ensuring public safety, securing personal privacy, and maintaining compliance with FAA regulation will become increasingly challenging as guidelines are altered and skies become more crowded.

\section {Solution}
By utilizing the /Gls{xyo-network}, automated drones operating independently of each other will be able to communicate their relative and absolute locations using a universal protocol. Drones that are not inherently able to communicate with one another can take advantage of the XYO Network and still interact through third-party intermediaries, including independent devices or other drones. Interactions between devices on the XYO Network are also recorded on the blockchain, a decentralized ledger. This means that all automated drones are held publicly accountable in the event of an accident, regulation infringement, or breach in safety or personal privacy through the availability of a permanent and unalterable record of all device interactions.

\section {How it Works}
Every drone that is connected to the /Gls{xyo-network} will include a device called a \Gls{sentinel}. Sentinels record and transmit \gls{heuristic} data like time, location, speed and temperature. They also communicate with other Sentinels and keep a record of these interactions. This history is transmitted to the blockchain via an XYO \Glspl{bridge}, which can either be included on the drones themselves, or as independent devices. The entire history of heuristic data and device interactions is archived on a decentralized, publicly accessible blockchain.

Drones operated by different companies or produced by different manufacturers may very likely lack a universal standard of wireless communication necessary to communicate directly with each other. The XYO Network is platform-agnostic and is not tied to any one radio broadcast band or communication protocol. This means that Bridges can act as middlemen between devices that would otherwise not be able to correspond with each other. Devices on the XYO Network can help improve each other's data, allowing for greater \gls{accuracy} among all drones. For example, if one drone uses GPS for location calculation, and another triangulates off of cell towers, comparing their data at the time of interaction will independently verify both devices' histories. A device on the XYO Network that doesn't have an independent geo-positioning system will also be able to use the drones' heuristics to confirm its own location.

Participation in the XYO Network is incentivized by XYO Tokens - Sentinels and Bridges are awarded XYO Tokens when the accurate information they provide to the XYO Network is accessed, as well as other devices on the XYO Network that are responsible for archiving and analyzing the data that is provided.  


\begin{center}
\line(1,0){50}
\end{center}


\clearpage
 
 \begin{thebibliography}{9}

\bibitem{nickelsburg-amazondrones}
Nickelsburg, Monica.
\textit{Jeff Bezos: Amazon Drones Will Find Landing Spots Using Symbols Printed Out By Customers}.
GeekWire, October 24, 2016.

\end{thebibliography}

\printglossaries

\end{document}
